# Assessing EWS with Individuals Sampled from Simulations

# Required Packages

```{r, include = FALSE}
require(scales)
require(evobiR)
require(gdata)
require(doBy)
require(ecp)
require(strucchange)
require(TTR)
require(moments)
require(tidyverse)
```

# Data

```{r}
## Constant temperature
constant1 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/constant.incidence.last.120.1.csv")
constant2 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/constant.incidence.last.120.2.csv")
constant3 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/constant.incidence.last.120.3.csv")
constant4 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/constant.incidence.last.120.4.csv")
constant5 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/constant.incidence.last.120.5.csv")
constant6 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/constant.incidence.last.120.6.csv")
constant7 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/constant.incidence.last.120.7.csv")
constant8 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/constant.incidence.last.120.8.csv")
constant9 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/constant.incidence.last.120.9.csv")
constant10 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/constant.incidence.last.120.10.csv")

constant.sims <- data.frame(
  time = seq(1, 120, 1),
  constant1[ , 2:101], 
  constant2[ , 2:101], 
  constant3[ , 2:101], 
  constant4[ , 2:101], 
  constant5[ , 2:101], 
  constant6[ , 2:101], 
  constant7[ , 2:101], 
  constant8[ , 2:101], 
  constant9[ , 2:101], 
  constant10[ , 2:101]
)

## Variable temperature
warming1 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/warming.incidence.last.120.1.csv")
warming2 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/warming.incidence.last.120.2.csv")
warming3 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/warming.incidence.last.120.3.csv")
warming4 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/warming.incidence.last.120.4.csv")
warming5 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/warming.incidence.last.120.5.csv")
warming6 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/warming.incidence.last.120.6.csv")
warming7 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/warming.incidence.last.120.7.csv")
warming8 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/warming.incidence.last.120.8.csv")
warming9 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/warming.incidence.last.120.9.csv")
warming10 <- read.csv("Kirk_Data/Sim_Pops_EWS_Analyses/warming.incidence.last.120.10.csv")

warming.sims <- data.frame(
  time = seq(1, 120, 1),
  warming1[ , 2:101], 
  warming2[ , 2:101], 
  warming3[ , 2:101], 
  warming4[ , 2:101], 
  warming5[ , 2:101], 
  warming6[ , 2:101], 
  warming7[ , 2:101], 
  warming8[ , 2:101], 
  warming9[ , 2:101], 
  warming10[ , 2:101]
)
```

# Sampling

Okay, so, if we look at `2_EpidemicModel-Stochastic.Rmd`, we can see that the SIDE model starts with 169 susceptible individuals, so that's our population size. Since this is a compartmental model, that should be constant. **BUT! We need to think about a couple things:**

-   **We don't know how many *Daphnia* were in the experimental population, so this might not be as comparative as we want it to be... Do we have an estimate of *proportion* of experimental population sampled?**

    -   **The experimental populations also wouldn't have stayed at a constant size, so the denominator should change...**

-   **Devin chose "large" individuals to enable quantification of parasite load; we're not doing "biased" sampling here**

-   **Need to make sure that there's no addition/removal happening in this model**

```{r}
rbinom(12, 1, 9/170) # Where 12 is the number of samples, 9 is the true prevalence, and 170 is N

# We want to count the number of 1s, and use that as our sampled prevalence
set.seed(123); infec.samp <- rbinom(12, 1, 9/170)
samp.prev <- length(which(infec.samp == 1))

## Okay, let's write a loop to take a look at this

N <- 170

## Constant
constant.sims.sampled.prev <- c()
for (i in 2:1001){
  prev.vec <- c()
  for (j in 1:120){
    set.seed(1); infec.samp <- rbinom(12, 1, constant.sims[j, i]/N)
    prev.vec[j] <- length(which(infec.samp == 1))
  }
  constant.sims.sampled.prev <- cbind(constant.sims.sampled.prev, prev.vec)
}

## Warming
warming.sims.sampled.prev <- c()
for (i in 2:1001){
  prev.vec <- c()
  for (j in 1:120){
    set.seed(1); infec.samp <- rbinom(12, 1, warming.sims[j, i]/N)
    prev.vec[j] <- length(which(infec.samp == 1))
  }
  warming.sims.sampled.prev <- cbind(warming.sims.sampled.prev, prev.vec)
}
```

# Plotting

Let's plot these to see what we're looking at!

```{r}
## Empirical Data
data <- read.csv("Kirk_Data/Epidemics_Data_Dryad/Kirk_et_al_epidemics_sampling_data.csv")
sub1 <- subset(data.sum, population == 1)
sub2 <- subset(data.sum, population == 2)
sub3 <- subset(data.sum, population == 3)
sub4 <- subset(data.sum, population == 4)
sub5 <- subset(data.sum, population == 5)
sub6 <- subset(data.sum, population == 6)
sub7 <- subset(data.sum, population == 7)
sub8 <- subset(data.sum, population == 8)

## Simulated Data w/ Sampling (15 populations of 1000)
plot(1:120, constant.sims.sampled.prev[ , 1], type = "l", col = alpha("#1434A4", 0.3),
     ylim = c(0, 8),
     main = "Constant", xlab = "Day", ylab = "Prevalence")
for (i in 2:15){
  lines(1:120, constant.sims.sampled.prev[ , i], col = alpha("#1434A4", 0.3))
}
lines(seq(1, 120, 3), sub1$status.sum, col = alpha("black", 0.6), lty = 3)
lines(seq(1, 120, 3), sub2$status.sum, col = alpha("black", 0.6), lty = 3)
lines(seq(1, 120, 3), sub3$status.sum, col = alpha("black", 0.6), lty = 3)
lines(seq(1, 120, 3), sub4$status.sum, col = alpha("black", 0.6), lty = 3)

plot(1:120, warming.sims.sampled.prev[ , 1], type = "l", col = alpha("#C21E56", 0.3),
     ylim = c(0, 8),
     main = "Warming", xlab = "Day", ylab = "Prevalence")
for (i in 2:15){
  lines(1:120, warming.sims.sampled.prev[ , i], col = alpha("#C21E56", 0.3))
}
lines(seq(1, 120, 3), sub5$status.sum, col = alpha("black", 0.6), lty = 3)
lines(seq(1, 120, 3), sub6$status.sum, col = alpha("black", 0.6), lty = 3)
lines(seq(1, 120, 3), sub7$status.sum, col = alpha("black", 0.6), lty = 3)
lines(seq(1, 120, 3), sub8$status.sum, col = alpha("black", 0.6), lty = 3)
```

Okay, that looks pretty good, and importantly, we're seeing a lot of zeros.

**NOTE: We could also remove the data such that we're "sampling" every third day?**

```{r}
samp.days <- seq(1, 120, 3)
constant.sims.sampled.prev.40 <- c()
for (i in 1:1000){
  prev.vec <- c()
  prev.vec <- constant.sims.sampled.prev[samp.days, i]
  constant.sims.sampled.prev.40 <- cbind(constant.sims.sampled.prev.40, prev.vec)
}
warming.sims.sampled.prev.40 <- c()
for (i in 1:1000){
  prev.vec <- c()
  prev.vec <- warming.sims.sampled.prev[samp.days, i]
  warming.sims.sampled.prev.40 <- cbind(warming.sims.sampled.prev.40, prev.vec)
}

## Plotting
plot(seq(1, 120, 3), constant.sims.sampled.prev.40[ , 1], type = "l", col = alpha("#1434A4", 0.3),
     ylim = c(0, 8),
     main = "Constant", xlab = "Day", ylab = "Prevalence")
for (i in 2:15){
  lines(seq(1, 120, 3), constant.sims.sampled.prev.40[ , i], col = alpha("#1434A4", 0.3))
}
lines(seq(1, 120, 3), sub1$status.sum, col = alpha("black", 0.6), lty = 3)
lines(seq(1, 120, 3), sub2$status.sum, col = alpha("black", 0.6), lty = 3)
lines(seq(1, 120, 3), sub3$status.sum, col = alpha("black", 0.6), lty = 3)
lines(seq(1, 120, 3), sub4$status.sum, col = alpha("black", 0.6), lty = 3)

plot(seq(1, 120, 3), warming.sims.sampled.prev.40[ , 1], type = "l", col = alpha("#C21E56", 0.3),
     ylim = c(0, 8),
     main = "Warming", xlab = "Day", ylab = "Prevalence")
for (i in 2:15){
  lines(seq(1, 120, 3), warming.sims.sampled.prev.40[ , i], col = alpha("#C21E56", 0.3))
}
lines(seq(1, 120, 3), sub5$status.sum, col = alpha("black", 0.6), lty = 3)
lines(seq(1, 120, 3), sub6$status.sum, col = alpha("black", 0.6), lty = 3)
lines(seq(1, 120, 3), sub7$status.sum, col = alpha("black", 0.6), lty = 3)
lines(seq(1, 120, 3), sub8$status.sum, col = alpha("black", 0.6), lty = 3)
```

# Computing EWS

## Metrics

```{r}
num.of.sims <- 10^3

# SD, Mean, Skewness, Kurtosis
constant.sims.sd.15 <- matrix(nrow = 35, ncol = num.of.sims)
constant.sims.mean.15 <- matrix(nrow = 35, ncol = num.of.sims)
constant.sims.sk.15 <- matrix(nrow = 35, ncol = num.of.sims)
constant.sims.kt.15 <- matrix(nrow = 35, ncol = num.of.sims)

warming.sims.sd.15 <- matrix(nrow = 35, ncol = num.of.sims)
warming.sims.mean.15 <- matrix(nrow = 35, ncol = num.of.sims)
warming.sims.sk.15 <- matrix(nrow = 35, ncol = num.of.sims)
warming.sims.kt.15 <- matrix(nrow = 35, ncol = num.of.sims)

for(i in 1:num.of.sims){
  constant.sims.sd.15[ ,i] <- SlidingWindow(FUN = "sd", data = constant.sims.sampled.prev.40[ ,i], window = 5, step = 1)
  constant.sims.mean.15[ ,i] <- SlidingWindow(FUN = "mean", data = constant.sims.sampled.prev.40[ ,i], window = 5, step = 1)
  constant.sims.sk.15[ ,i] <- SlidingWindow(FUN = "skewness", data = constant.sims.sampled.prev.40[ ,i], window = 5, step = 1)
  constant.sims.kt.15[ ,i] <- SlidingWindow(FUN = "kurtosis", data = constant.sims.sampled.prev.40[ ,i], window = 5, step = 1)
}

for(i in 1:num.of.sims){
  warming.sims.sd.15[ ,i] <- SlidingWindow(FUN = "sd", data = warming.sims.sampled.prev.40[ ,i], window = 5, step = 1)
  warming.sims.mean.15[ ,i] <- SlidingWindow(FUN = "mean", data = warming.sims.sampled.prev.40[ ,i], window = 5, step = 1)
  warming.sims.sk.15[ ,i] <- SlidingWindow(FUN = "skewness", data = warming.sims.sampled.prev.40[ ,i], window = 5, step = 1)
  warming.sims.kt.15[ ,i] <- SlidingWindow(FUN = "kurtosis", data = warming.sims.sampled.prev.40[ ,i], window = 5, step = 1)
}

## Variance
constant.sims.var.15 <- constant.sims.sd.15*constant.sims.sd.15
warming.sims.var.15 <- warming.sims.sd.15*warming.sims.sd.15

## Co-Efficient of Variation
constant.sims.cv.15 <- constant.sims.sd.15/constant.sims.mean.15
warming.sims.cv.15 <- warming.sims.sd.15/warming.sims.mean.15

## Index of Dispersion
constant.sims.id.15 <- constant.sims.var.15/constant.sims.mean.15
warming.sims.id.15 <- warming.sims.var.15/warming.sims.mean.15

## First Difference Variance
constant.sims.fdv.15 <- matrix(ncol = num.of.sims, nrow = 35)
warming.sims.fdv.15 <- matrix(ncol = num.of.sims, nrow = 35)

for(i in 1:num.of.sims){
  for(j in 2:35){
    constant.sims.fdv.15[j - 1,i] <- constant.sims.var.15[j,i] - constant.sims.var.15[j - 1,i]
    warming.sims.fdv.15[j - 1,i] <- warming.sims.var.15[j,i] - warming.sims.var.15[j - 1,i]
  }
}
constant.sims.fdv.15 <- constant.sims.fdv.15[1:34, ]
warming.sims.fdv.15 <- warming.sims.fdv.15[1:34, ]

## Autocorrelation and Autocovariance
constant.sims.ac.15 <- matrix(ncol = num.of.sims, nrow = 40)
constant.sims.acv.15 <- matrix(ncol = num.of.sims, nrow = 40)

for(j in 1:num.of.sims){
  for(i in 1:35){
    window.start <- i
    window.end <- i + 4
    
    segment <- constant.sims.sampled.prev.40[c(window.start:window.end),j]
    
    constant.sims.ac.15[i, j] <- acf(segment, plot = FALSE, type = "correlation")[[1]][2]
    constant.sims.acv.15[i, j] <- acf(segment, plot = FALSE, type = "covariance")[[1]][2]
  }
}

warming.sims.ac.15 <- matrix(ncol = num.of.sims,nrow = 40)
warming.sims.acv.15 <- matrix(ncol = num.of.sims,nrow = 40)

for(j in 1:num.of.sims){
  for(i in 1:35){
    window.start <- i
    window.end <- i + 4
    
    segment <- warming.sims.sampled.prev.40[c(window.start:window.end),j]
    
    warming.sims.ac.15[i, j] <- acf(segment, plot = FALSE, type = "correlation")[[1]][2]
    warming.sims.acv.15[i, j] <- acf(segment, plot = FALSE, type = "covariance")[[1]][2]
  }
}

## Decay Time
constant.sims.dt.15 <- matrix(ncol = num.of.sims, nrow = 35)
warming.sims.dt.15 <- matrix(nco = num.of.sims, nrow = 35)

for(i in 1:num.of.sims){
  for(j in 1:35){
    suppressWarnings(constant.sims.dt.15[j, i] <- -j/log(constant.sims.ac.15[j, i]))
    suppressWarnings(warming.sims.dt.15[j, i] <- -j/log(warming.sims.ac.15[j, i]))
  }
}
```

## Kendall's Tau

```{r}
constant.sims.var.15 <- constant.sims.var.15[1:15, ]
constant.sims.mean.15 <- constant.sims.mean.15[1:15, ]
constant.sims.cv.15 <- constant.sims.cv.15[1:15, ]
constant.sims.sk.15 <- constant.sims.sk.15[1:15, ]
constant.sims.kt.15 <- constant.sims.kt.15[1:15, ]
constant.sims.id.15 <- constant.sims.id.15[1:15, ]
constant.sims.ac.15 <- constant.sims.ac.15[1:15, ]
constant.sims.acv.15 <- constant.sims.acv.15[1:15, ]
constant.sims.fdv.15 <- constant.sims.fdv.15[1:15, ]
constant.sims.dt.15 <- constant.sims.dt.15[1:15, ]

warming.sims.var.15 <- warming.sims.var.15[1:15, ]
warming.sims.mean.15 <- warming.sims.mean.15[1:15, ]
warming.sims.cv.15 <- warming.sims.cv.15[1:15, ]
warming.sims.sk.15 <- warming.sims.sk.15[1:15, ]
warming.sims.kt.15 <- warming.sims.kt.15[1:15, ]
warming.sims.id.15 <- warming.sims.id.15[1:15, ]
warming.sims.ac.15 <- warming.sims.ac.15[1:15, ]
warming.sims.acv.15 <- warming.sims.acv.15[1:15, ]
warming.sims.fdv.15 <- warming.sims.fdv.15[1:15, ]
warming.sims.dt.15 <- warming.sims.dt.15[1:15, ]

constant.sims.var.15.tau <- c()
constant.sims.mean.15.tau <- c()
constant.sims.cv.15.tau <- c()
constant.sims.sk.15.tau <- c()
constant.sims.kt.15.tau <- c()
constant.sims.id.15.tau <- c()
constant.sims.ac.15.tau <- c()
constant.sims.acv.15.tau <- c()
constant.sims.fdv.15.tau <- c()
constant.sims.dt.15.tau <- c()

warming.sims.var.15.tau <- c()
warming.sims.mean.15.tau <- c()
warming.sims.cv.15.tau <- c()
warming.sims.sk.15.tau <- c()
warming.sims.kt.15.tau <- c()
warming.sims.id.15.tau <- c()
warming.sims.ac.15.tau <- c()
warming.sims.acv.15.tau <- c()
warming.sims.fdv.15.tau <- c()
warming.sims.dt.15.tau <- c()

time.15 <- c(1:15)

for(i in 1:num.of.sims){
  constant.sims.mean.15.tau[i] <- cor(constant.sims.mean.15[ , i], time.15, method = "kendall")
  constant.sims.sk.15.tau[i] <- cor(constant.sims.sk.15[ , i], time.15, method = "kendall")
  constant.sims.kt.15.tau[i] <- cor(constant.sims.kt.15[ , i], time.15, method = "kendall")
  constant.sims.var.15.tau[i] <- cor(constant.sims.var.15[ , i], time.15, method = "kendall")
  constant.sims.cv.15.tau[i] <- cor(constant.sims.cv.15[ , i], time.15, method = "kendall")
  constant.sims.id.15.tau[i] <- cor(constant.sims.id.15[ , i], time.15, method = "kendall")
  constant.sims.fdv.15.tau[i] <- cor(constant.sims.fdv.15[ , i], time.15, method = "kendall")
  constant.sims.ac.15.tau[i] <- cor(constant.sims.ac.15[ , i], time.15, method = "kendall")
  constant.sims.acv.15.tau[i] <- cor(constant.sims.acv.15[ , i], time.15, method = "kendall")
  constant.sims.dt.15.tau[i] <- cor(constant.sims.dt.15[ , i], time.15, method = "kendall")
  
  warming.sims.mean.15.tau[i] <- cor(warming.sims.mean.15[ , i], time.15, method = "kendall")
  warming.sims.sk.15.tau[i] <- cor(warming.sims.sk.15[ , i], time.15, method = "kendall")
  warming.sims.kt.15.tau[i] <- cor(warming.sims.kt.15[ , i], time.15, method = "kendall")
  warming.sims.var.15.tau[i] <- cor(warming.sims.var.15[ , i], time.15, method = "kendall")
  warming.sims.cv.15.tau[i] <- cor(warming.sims.cv.15[ , i], time.15, method = "kendall")
  warming.sims.id.15.tau[i] <- cor(warming.sims.id.15[ , i], time.15, method = "kendall")
  warming.sims.fdv.15.tau[i] <- cor(warming.sims.fdv.15[ , i], time.15, method = "kendall")
  warming.sims.ac.15.tau[i] <- cor(warming.sims.ac.15[ , i], time.15, method = "kendall")
  warming.sims.acv.15.tau[i] <- cor(warming.sims.acv.15[ , i], time.15, method = "kendall")
  warming.sims.dt.15.tau[i] <- cor(warming.sims.dt.15[ , i], time.15, method = "kendall")
}
```

### Plotting

```{r}
cols <- c(rep("#1434A4", 1000), rep("#C21E56", 1000))

## Mean
mean <- data.frame(
  treatment = c(rep("Constant", 1000), rep("Warming", 1000)),
  k.tau = c(constant.sims.mean.15.tau, warming.sims.mean.15.tau)
)
ggplot(mean, aes(x = treatment, y = k.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Treatment") +
  ylab("Kendall's Tau (Mean)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

## Variance
var <- data.frame(
  treatment = c(rep("Constant", 1000), rep("Warming", 1000)),
  k.tau = c(constant.sims.var.15.tau, warming.sims.var.15.tau)
)
ggplot(var, aes(x = treatment, y = k.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Treatment") +
  ylab("Kendall's Tau (Variance)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

## Skewness
sk <- data.frame(
  treatment = c(rep("Constant", 1000), rep("Warming", 1000)),
  k.tau = c(constant.sims.sk.15.tau, warming.sims.sk.15.tau)
)
ggplot(sk, aes(x = treatment, y = k.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Treatment") +
  ylab("Kendall's Tau (Skewness)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

## Kurtosis
kt <- data.frame(
  treatment = c(rep("Constant", 1000), rep("Warming", 1000)),
  k.tau = c(constant.sims.kt.15.tau, warming.sims.kt.15.tau)
)
ggplot(kt, aes(x = treatment, y = k.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Treatment") +
  ylab("Kendall's Tau (Kurtosis)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

## Co-Efficient of Variation
cv <- data.frame(
  treatment = c(rep("Constant", 1000), rep("Warming", 1000)),
  k.tau = c(constant.sims.cv.15.tau, warming.sims.cv.15.tau)
)
ggplot(cv, aes(x = treatment, y = k.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Treatment") +
  ylab("Kendall's Tau (Co-Efficient of Variation)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

## Index of Dispersion
id <- data.frame(
  treatment = c(rep("Constant", 1000), rep("Warming", 1000)),
  k.tau = c(constant.sims.id.15.tau, warming.sims.id.15.tau)
)
ggplot(id, aes(x = treatment, y = k.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Treatment") +
  ylab("Kendall's Tau (Index of Dispersion)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

## First Difference Variance
fdv <- data.frame(
  treatment = c(rep("Constant", 1000), rep("Warming", 1000)),
  k.tau = c(constant.sims.fdv.15.tau, warming.sims.fdv.15.tau)
)
ggplot(fdv, aes(x = treatment, y = k.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Treatment") +
  ylab("Kendall's Tau (First Difference Variance)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

## Autocorrelation
ac <- data.frame(
  treatment = c(rep("Constant", 1000), rep("Warming", 1000)),
  k.tau = c(constant.sims.ac.15.tau, warming.sims.ac.15.tau)
)
ggplot(ac, aes(x = treatment, y = k.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Treatment") +
  ylab("Kendall's Tau (Autocorrelation)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

## Autocovariance
acv <- data.frame(
  treatment = c(rep("Constant", 1000), rep("Warming", 1000)),
  k.tau = c(constant.sims.acv.15.tau, warming.sims.acv.15.tau)
)
ggplot(acv, aes(x = treatment, y = k.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Treatment") +
  ylab("Kendall's Tau (Autocovariance)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

## Decay Time
dt <- data.frame(
  treatment = c(rep("Constant", 1000), rep("Warming", 1000)),
  k.tau = c(constant.sims.dt.15.tau, warming.sims.dt.15.tau)
)
ggplot(dt, aes(x = treatment, y = k.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Treatment") +
  ylab("Kendall's Tau (Decay Time)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

### Median Trend Coefficients

```{r}
med.constant.sims.mean.15.tau <- median(constant.sims.mean.15.tau, na.rm = TRUE)
med.constant.sims.sk.15.tau <- median(constant.sims.sk.15.tau, na.rm = TRUE)
med.constant.sims.kt.15.tau <- median(constant.sims.kt.15.tau, na.rm = TRUE)
med.constant.sims.var.15.tau <- median(constant.sims.var.15.tau, na.rm = TRUE)
med.constant.sims.cv.15.tau <- median(constant.sims.cv.15.tau, na.rm = TRUE)
med.constant.sims.id.15.tau <- median(constant.sims.id.15.tau, na.rm = TRUE)
med.constant.sims.fdv.15.tau <- median(constant.sims.fdv.15.tau, na.rm = TRUE)
med.constant.sims.ac.15.tau <- median(constant.sims.ac.15.tau, na.rm = TRUE)
med.constant.sims.acv.15.tau <- median(constant.sims.acv.15.tau, na.rm = TRUE)
med.constant.sims.dt.15.tau <- median(constant.sims.dt.15.tau, na.rm = TRUE)
range(c(med.constant.sims.mean.15.tau, med.constant.sims.sk.15.tau, 
      med.constant.sims.kt.15.tau, med.constant.sims.var.15.tau,
      med.constant.sims.cv.15.tau, med.constant.sims.id.15.tau,
      med.constant.sims.fdv.15.tau, med.constant.sims.ac.15.tau,
      med.constant.sims.acv.15.tau, med.constant.sims.dt.15.tau), na.rm = TRUE)

med.warming.sims.mean.15.tau <- median(warming.sims.mean.15.tau, na.rm = TRUE)
med.warming.sims.sk.15.tau <- median(warming.sims.sk.15.tau, na.rm = TRUE)
med.warming.sims.kt.15.tau <- median(warming.sims.kt.15.tau, na.rm = TRUE)
med.warming.sims.var.15.tau <- median(warming.sims.var.15.tau, na.rm = TRUE)
med.warming.sims.cv.15.tau <- median(warming.sims.cv.15.tau, na.rm = TRUE)
med.warming.sims.id.15.tau <- median(warming.sims.id.15.tau, na.rm = TRUE)
med.warming.sims.fdv.15.tau <- median(warming.sims.fdv.15.tau, na.rm = TRUE)
med.warming.sims.ac.15.tau <- median(warming.sims.ac.15.tau, na.rm = TRUE)
med.warming.sims.acv.15.tau <- median(warming.sims.acv.15.tau, na.rm = TRUE)
med.warming.sims.dt.15.tau <- median(warming.sims.dt.15.tau, na.rm = TRUE)
range(c(med.warming.sims.mean.15.tau, med.warming.sims.sk.15.tau, 
      med.warming.sims.kt.15.tau, med.warming.sims.var.15.tau,
      med.warming.sims.cv.15.tau, med.warming.sims.id.15.tau,
      med.warming.sims.fdv.15.tau, med.warming.sims.ac.15.tau,
      med.warming.sims.acv.15.tau, med.warming.sims.dt.15.tau), na.rm = TRUE)
```

## AUC

```{r}
AUC_mean_15 <- calc_auc(warming.sims.mean.15.tau, constant.sims.mean.15.tau); AUC_mean_15
AUC_sk_15 <- calc_auc(warming.sims.sk.15.tau, constant.sims.sk.15.tau); AUC_sk_15
AUC_kt_15 <- calc_auc(warming.sims.kt.15.tau, constant.sims.kt.15.tau); AUC_kt_15
AUC_var_15 <- calc_auc(warming.sims.var.15.tau, constant.sims.var.15.tau); AUC_var_15
AUC_cv_15 <- calc_auc(warming.sims.cv.15.tau, constant.sims.cv.15.tau); AUC_cv_15
AUC_id_15 <- calc_auc(warming.sims.id.15.tau, constant.sims.id.15.tau); AUC_id_15
AUC_fdv_15 <- calc_auc(warming.sims.fdv.15.tau, constant.sims.fdv.15.tau); AUC_fdv_15
AUC_ac_15 <- calc_auc(warming.sims.ac.15.tau, constant.sims.ac.15.tau); AUC_ac_15
AUC_acv_15 <- calc_auc(warming.sims.acv.15.tau, constant.sims.acv.15.tau); AUC_acv_15
AUC_dt_15 <- calc_auc(warming.sims.dt.15.tau, constant.sims.dt.15.tau); AUC_dt_15
```

### Plotting

```{r}
metrics <- c("mean", "skewness", "kurtosis", "variance", "cv", "id", "fdv", "cor", "acv", "dt")

AUC_15 <- c(AUC_mean_15, AUC_sk_15, AUC_kt_15, AUC_var_15, AUC_cv_15, 
           AUC_id_15, AUC_fdv_15, AUC_ac_15 ,AUC_acv_15, AUC_dt_15)

metrics_full <- c("Mean", "Skewness", "Kurtosis", "Variance", "Coefficient of Variation", "Index of Dispersion", "First Difference Variance", "Autocorrelation", "Autocovariance", "Decay Time")

## Plot 
par(mar = c(11, 4.1, 4.1, 2.1))
plot(1:10, AUC_15, type = "p", 
     main = "Simulated Data", xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = "red3", pch = 19)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2)
mtext("(After accounting for the effects of experimental sampling.)", side = 3, line = 0.4)
```
